Verifying synchronous distributed algorithms using IVy

### 2018-08-06 paper/paper.tex
- page 8, section (III.iii): explicitly state that this algorithm has been 	proven correct in Lynch's book, and that the proofs are shortly presented 	here as well

\noindent What follows is a proof of the correctness of the \textit{Floodset} algorithm to illustrate the principles behind it.\\
\\
\noindent Let $W_i(j)$ denote the value of $W$ for node $i$ in round $j$. The following Lemmas apply:\\

>>>>

\noindent What follows is a proof of the correctness of the \textit{Floodset} algorithm to illustrate the principles behind it. It has already been proven correct in \cite{refNancy}. This work presents a slightly varied approach to the proofs of \cite{refNancy} founded on the same general proof ideas.\\
\\
\noindent Let $W_i(j)$ denote the value of $W$ for node $i$ in round $j$. The following Lemmas apply:\\
